% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,9pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Christopher M. Palce}& https://cmpalce.com\\
09565641269 (cell)&  christopher.palce.10@gmail.com \\
Quezon City, PH 1116& https://github.com/eclap\\
\end{tabular*}
\\

\vspace{0.1in} 

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Eastvantage}{Fort Legends Tower}{Senior Backend Developer}{ June 2021 - Present}
	\begin{itemize}
        \resitem{Develop new features for client's public web application.}
        \resitem{Maintains web application by fixing bugs, integrating unit testing and refactoring.}
        \resitem{Handles deployments and production-level related tasks.}
        \resitem{Participate in planning and provides input for solutions and targets.}
        \resitem{\textit{Laravel, ReactJS, PostgreSQL}}
	\end{itemize}
\item
	\ressubheading{RingCentral Inc.}{World Wide Corporate Center, Mandaluyong}{Senior NOC Tools Developer}{September 2015 - June 2021}
	\begin{itemize}
        \resitem{Maintains and develop new features in an internal web application that is being used to monitor the health status of company’s products and services.}
		\resitem{Rewrote legacy web application that contributed in the tool’s increased reliability and productivity.}
        \resitem{\textit{Laravel, VueJS, MySQL}}
	\end{itemize}
\item
	\ressubheading{Rekursv Inc.}{Burgundy Tower, Makati}{Software Developer}{September 2012 - September 2015}
	\begin{itemize}
		\resitem{Built an educational tech application. Both in web and mobile (android) platform for taking quizzes and assessing students’ performance.}
        \resitem{\textit{AngularJS, ExpressJS, MySQL, MongoDB, Java Jersey, Java Android}}
	\end{itemize}
\item
	\ressubheading{Pinoymed.com}{Medical City, Ortigas}{Software Developer}{March 2012 - September 2012}
	\begin{itemize}
		\resitem{Built a website that focuses in medical-health content using PhpBB CMS.}
        \resitem{\textit{PhpBB, MySQL, Javascript}}
	\end{itemize}
\item
	\ressubheading{Tradeport Inc.}{San Juan City}{Web Developer}{February 2011 - February 2012}
	\begin{itemize}
		\resitem{Built a web platform for DVD and Blu-ray rentals called Blupass that is initially part of Samsung’s promo but eventually became the company’s own business.}
        \resitem{\textit{PHP, Javascript, MySQL, CSS3}}
	\end{itemize}
\item
	\ressubheading{Private Scandinavian Sparkase Global Processing System}{The Fort, Taguig}{Web Developer}{June 2010 - November 2010}
	\begin{itemize}
		\resitem{Part of the team that worked on a website about forex trading.}
		\resitem{Automated forex trading in MT4 platform based on algorithms provided by the company.}
        \resitem{\textit{CodeIgniter, jQuery, CSS3, MySQL, C++}}
	\end{itemize}
\end{itemize}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{University of the Philippines Los Ba\~nos}{Los Ba\~nos, Laguna}{Bachelor of Science in Computer Science}{Jun. 2004 - May. 2010}
	\begin{itemize}
		\resitem{Senior Thesis: Infectious Disease Epidemic Simulator}
	\end{itemize}

\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
PHP, Javascript/NodeJS
\item[Database:]
SQL
\item[Operating Systems:]
Linux 
\item[Frameworks:]
Laravel, ExpressJS, VueJS, ReactJS
\item[Other Tools:]
Unit Testing, TDD, Docker, Git
\item[Other Languages and Frameworks:]
Python, Django, Socket.IO, Angular 1, Java, Android, Jersey, MongoDB
\end{description}

\pagebreak

\end{document}
